---
title: "``annotate_y_axis``: Annotations in the axis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
```


#### Description
Annotations in the axis

#### Usage
<pre><code>
annotate_y_axis(label, y, side = waiver(), print_label = TRUE,
print_value = TRUE, print_both = TRUE, parsed = FALSE, ...)
annotate_x_axis(label, x, side = waiver(), print_label = TRUE,
print_value = TRUE, print_both = TRUE, parsed = FALSE, ...)
</code></pre>

#### Arguments
* ``label``: Text to print
* ``y``, ``x``: Position of the annotation.
* ``side``: left or right, or top or bottom side to print annotation
* ``print_label``, ``print_value``, ``print_both`` Logical; what to show on annotation. Label and/or value. print_both is short-
cut for setting both print_label and print_value. When both is TRUE, uses argument sep to separate the label and value.
* ``parsed`` Logical (default FALSE), when TRUE, uses mathplot for outputting expressions. See section "Showing values".
* ``...`` Style settings for label and tick: colour, hjust, vjust, size, fontface, family, rot. When ``waiver()`` (default), the relevant theme element is used.
* Showing values: See plotmath for using mathematical expressions. The function uses a simple replacement strategy where the literal strings .(y) and .(val) are replaced by the value after round of to a number of digits, as given by argument digits.

#### Examples
```{r}
library(ggplot2)
p <- ggplot(mtcars, aes(mpg, hp, colour=disp)) + geom_point()
l <- p + annotate_y_axis('mark at', y=200, tick=TRUE)
l
(l + annotate_x_axis('| good economy ->', x=25, print_value=FALSE, hjust=0, tick=TRUE))
l + annotate_y_axis("x^2 == .(y)", y=150, parsed=FALSE, tick=FALSE) +
annotate_y_axis("x^2 + bar(x) == .(y)", y=mean(mtcars$hp), parsed=TRUE, tick=TRUE)
```


```{r}
l + annotate_y_axis("bar(x) == .(y)", y = mean(mtcars$hp), parsed=TRUE, tick=FALSE)
# use double equal signs, or the output becomes '=(...)' for some reason.
l + annotate_y_axis('this is midway', y=sum(range(mtcars$hp))/2, print_value = FALSE, side='left')
```


```{r}
# work around if an axis only contains parsed expressions
p + annotate_y_axis("bar(x) == .(y)", y = mean(mtcars$hp), parsed=TRUE, tick=FALSE) +
   annotate_y_axis("some long string", y=100, tick=FALSE, print_value=FALSE, colour=NA)
# Works together with other functions
p <- p + theme_light() + theme(panel.border=element_blank(),
axis.line = element_line(),
axis.ticks = element_line(colour='black'))
```

```{r}
p + coord_capped_cart(bottom='right') +
annotate_y_axis('More than I\ncan afford', y=125,
print_value=FALSE, tick=TRUE)
```
