
## ``brackets_horizontal```:  Axis brackets instead of axis ticks and lines

#### Description
To be used with coord_flex_cart, coord_capped_cart, etc. for displaying brackets instead of
the axis ticks and lines.

#### Usage
<pre><code>
brackets_horizontal(direction = c("up", "down"), length = unit(0.05, "npc"), tick.length = waiver())
brackets_vertical(direction = c("left", "right"), length = unit(0.05, "npc"), tick.length = waiver())
</code></pre>

#### Arguments
* ``direction``: Which way should the opening side of the brackets point? up, down, left, or right?
* ``length``: Length of the unit, parallel with axis line.
* ``tick.length``: Height (width) of x-axis (y-axis) bracket. If waiver() (default), use axis.ticks.length from theme.


#### Examples
```{r}
library(ggplot2)
p <- ggplot(mpg, aes(as.factor(cyl), hwy, colour=class)) +
geom_point(position=position_jitter(width=0.3)) +
theme_bw() +
theme(panel.border = element_blank(), axis.line = element_line())
p
```

```{r}
p <- p + coord_flex_cart(bottom=brackets_horizontal(length=unit(0.08, 'npc')))6
coord_capped_cart
p
# However getting the correct width is a matter of tweaking either length or
# position_jitter...
# A further adjustment,
p + theme(panel.grid.major.x = element_blank())
```
#### Details
The looks of the brackets are taken from theme(axis.ticks), or theme(axis.ticks.x) and
theme(axis.ticks.y), respectively.
It does not re-calculate tick marks, but lets scale_x_* and scale_y_* calculate and draw ticks and
labels, and then modifies the ticks with brackets.
Both length and tick.length accepts a numeric scalar instead of a unit object that is interpreted
as an "npc" unit.
See Also
unit
