---
title: "``coord_flex_cart``: Cartesian coordinates with flexible options for drawing axes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
```

#### Description

Allows user to inject a function for drawing axes, such as ``capped_horizontal`` or ``brackets_horizontal``.

#### Usage
<pre><code>
coord_flex_cart(xlim = NULL, ylim = NULL, expand = TRUE, top = waiver(), left = waiver(), bottom = waiver(),
right = waiver())
coord_flex_flip(xlim = NULL, ylim = NULL, expand = TRUE, top = waiver(), left = waiver(), bottom = waiver(),
right = waiver())
coord_flex_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, top = waiver(), left = waiver(),
bottom = waiver(), right = waiver())
</code></pre>

#### Arguments
* xlim, ylim Limits for the x and y axes.
* expand If TRUE, the default, adds a small expansion factor to the limits to ensure that
data and axes don’t overlap. If FALSE, limits are taken exactly from the data or
xlim/ylim.
* top, left, bottom, right Function for drawing axis lines, ticks, and labels, use e.g. capped_horizontal
or brackets_horizontal.
* ratio: aspect ratio, expressed as y / x.


#### Examples
```{r}
library(ggplot2)
# A standard plot
p <- ggplot(mtcars, aes(disp, wt)) +
geom_point() +
geom_smooth() + theme(panel.border=element_blank(), axis.line=element_line())
# We desire that left axis does not extend beyond '6'
# and the x-axis is unaffected
p + coord_capped_cart(left='top')
# Specifying 'bottom' caps the axis with at most the length of 'gap'
p + coord_capped_cart(left='top', bottom='none')
# We can specify a ridiculus large 'gap', but the lines will always
# protrude to the outer most ticks.element_render
9
p + coord_capped_cart(left='top', bottom='none', gap=2)
# We can use 'capped_horizontal' and 'capped_vertical' to specify for
# each axis individually.
```

```{r}
p + coord_capped_cart(left='top', bottom=capped_horizontal('none', gap=2))
# At this point we might as well drop using the short-hand and go full on:
p + coord_flex_cart(left=brackets_vertical(), bottom=capped_horizontal('left'))
# Also works with secondary axes:
```

```{r}
p + scale_y_continuous(sec.axis=sec_axis(~5*., name='wt times 5')) +
coord_flex_cart(left=brackets_vertical(), bottom=capped_horizontal('right'),
right=capped_vertical('both', gap=0.02))
```

```{r}
# Supports the usual 'coord_fixed':
p + coord_flex_fixed(ratio=1.2, bottom=capped_horizontal('right'))
# and coord_flip:
p + coord_flex_flip(ylim=c(2,5), bottom=capped_horizontal('right'))
```
#### Details
NB! A panel-border is typically drawn on top such that it covers tick marks, grid lines, and axis
lines. Many themes also do not draw axis lines. To ensure the modified axis lines are visible, use
theme(panel.border=element_blank(), axis.line=element_line()).
User defined functions
The provided function in top, right, bottom, and left defaults to render_axis which is defined
in ‘ggplot2/R/coord-.r’, which in turns calls guide_axis (see ‘ggplot2/R/guides-axis.r’).
The provided function is with the arguments scale_details, axis, scale, position, and theme,
and the function should return an absoluteGrob object.
For examples of modifying the drawn object, see e.g. capped_horizontal or brackets_horizontal.