---
title: "``lemon::dot``- Create paths that are safe from changing working directory."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
```



#### Description
The ``.dot`` functions creates functions that allows relative-like specification of paths, but are safe from changing working directory.

#### Usage
<pre><code>
.dot(x, root = getwd(), mustExist = FALSE, relative = FALSE, create = TRUE)
.dot2(names, quiet = FALSE, ...)
</code></pre>

#### Arguments
* ``x``: File path that is appended to BASEDIR.
* ``root``: Root of your working directory, from which x is relative too.
* ``mustExist``: Logical value; if TRUE and the resulting path does not exist, it raises an error.
* ``relative``: For ``.dot``, sets default for the returned function. For the returned function, when ``TRUE``, the function returns a path relative to root.
* ``create``: Logical values, creates the target directory when TRUE (default).
* ``names``: Character vector of names
* ``quiet``: Logical value, suppresses output to ``stdout()`` when TRUE.
* ``...``: Arguments passed on to .dot.

#### Value
A function that returns file paths constructed from root, x, and ....
Side effect: It creates the directory.

#### Examples
```{r}
.data <- .dot('data')
.data('input.txt')
.data(c('a.txt','b.txt'))
.dot2(c('rawdata','results'))
.rawdata('rawfile.csv')
.results('myresults.txt')
```

Create paths that are safe from changing working directory.
