---
title: "``geom_siderange``: Display range of data in side of plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
```

#### Description
Projects data onto horizontal or vertical edge of panels.

#### Usage
<pre><code>
geom_siderange(mapping = NULL, data = NULL, stat = "identity",
position = "identity", ..., distance = 3, arrow = NULL,
lineend = "butt", sides = "bl", start = NA, end = NA,
na.rm = FALSE, show.legend = NA, inherit.aes = TRUE)
</code></pre>

#### Arguments
* ``mapping``: Set of aesthetic mappings created by ``aes`` or ``aes_``.
* ``data``: The data to be displayed in this layer.
* ``stat``: The statistical transformation to use on the data for this layer, as a string.
* ``position``: Position adjustment, either as a string, or the result of a call to a position adjustment function (e.g. position_jitter). Both lines and points gets the same adjustment (this is where the function excels over ``geom_point() + geom_line()``).
* ... other arguments passed on to layer.
* ``distance``: Distance between edge of panel and lines, and distance between lines, in multiples of line widths, see description.
* ``arrow``: Arrow specification, as created by arrow.
* ``lineend``: Line end style (round, butt, square).
* ``sides``: Character including top, right, bottom, and/or left, indicating which side to project data onto.
* start, end Adds a symbol to either end of the siderange. start corresponds to minimal value, end to maximal value.
* ``na.rm``: If FALSE (default), missing values are removed with a warning. If TRUE, missing values are silently removed.
* ``show.legend``: Logical. Should this layer be included in the legends? NA (default), includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.
* ``inherit.aes``: If FALSE, overrides the default aesthetic, rather than combining with them. This is most useful for helper functions that define both data and aesthetics and shouldn’t inherit behaviour from the default plot specification.

#### Examples
```{r}
library(ggplot2)
x <- rnorm(25)
df <- data.frame(x=x, y=x+rnorm(25, sd=0.2),
a=sample(c('horse','goat'), 25, replace=TRUE),
stringsAsFactors = FALSE)
df$y <- with(df, ifelse(y > 1 & a=='horse', 1, y))
(p <- ggplot(df, aes(x=x, y=y, colour=a)) + geom_point(shape=1))
p + geom_siderange(start=19)
# Capping the sideranges with different symbols:
p + geom_siderange(start=19, end=22, fill='black', sides='b') + geom_siderange(sides='tl')
# It also works with facets
p <- ggplot(mpg, aes(displ, hwy, colour=fl)) +
geom_point() +
facet_wrap(~class, nrow = 4)
p + geom_siderange()
```

#### Details
The geom_siderange projects the data displayed in the panel onto the sides, using the same aes-
thetics. It has the added capability of potting a symbol at either end of the line, and lines are offset
from the edge and each other.
To display a symbol, specify an integer for either start or end. See the list for pch in points for values to use. The argumetns start and end also accepts a list object with named entries pch, alpha, stroke, and fill, which correspond to the usual aesthetics, as well as a special named entry, sizer (note the extra ’r’). This last entry is a multiplier for enlarging the symbol relative to
the linewidth, as the aesthetic size affects both linewidth and symbol size.
The distance between the panel’s edge and sideranges are specified by the argument distance. If
a symbol is specified, the linewidth is further expanded to cover the width of the symbol (including
sizer).

#### Aesthetics
The geom understands the following aesthetics (required are in bold):
• x
• y
• alpha
• colour
• fill (if a symbol is applied with start or end
• groupget_panel_range
15
• linetype
• size
• stroke
See Also
geom_rug

