---
title: "``geom_pointpath``: Connected points"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
```

#### Description
``geom_pointpath`` combines ``geom_point`` and ``geom_path``, such that a) when jittering is used, both lines and points stay connected, and b) provides a visual effect by adding a small gap between the point and the end of line. ``geom_pointline`` combines ``geom_point`` and ``geom_path``.

#### Usage
<pre><code>
geom_pointpath(mapping = NULL, data = NULL, stat = "identity",
position = "identity", na.rm = FALSE, show.legend = NA,
 inherit.aes = TRUE, distance = unit(3, "pt"), shorten = 0.5,
 threshold = 0.1, lineend = "butt", linejoin = "round",
 linemitre = 1, linesize = 0.5, linecolour = waiver(),
 linecolor = waiver(), arrow = NULL, ...)

geom_pointline(mapping = NULL, data = NULL, stat = "identity",
 position = "identity", na.rm = FALSE, show.legend = NA,
 inherit.aes = TRUE, distance = unit(3, "pt"), shorten = 0.5,
 threshold = 0.1, lineend = "butt", linejoin = "round",
 linemitre = 1, linesize = 0.5, linecolour = waiver(),
 linecolor = waiver(), arrow = NULL, ...)

geom_pointrangeline(mapping = NULL, data = NULL, stat = "identity",
 position = "identity", na.rm = FALSE, show.legend = NA,
 inherit.aes = TRUE, distance = unit(3, "pt"), lineend = "butt",
 linejoin = "round", linemitre = 1, linesize = 0.5,
 linecolour = waiver(), linecolor = waiver(), arrow = NULL, ...)
</code></pre>

#### Arguments

* ``mapping``: Set of aesthetic mappings created by aes or aes_.
* ``data``: The data to be displayed in this layer.
* ``stat``: The statistical transformation to use on the data for this layer, as a string.
* ``position``: Position adjustment, either as a string, or the result of a call to a position adjustment function (e.g. position_jitter). Both lines and points gets the same adjustment (this is where the function excels over ``geom_point() + geom_line()``).
na.rm If FALSE (default), missing values are removed with a warning. If TRUE, missing values are silently removed.
* ``show.legend``: Logical. Should this layer be included in the legends? NA (default), includes if any aesthetics are mapped. FALSE never includes, and TRUE always includes.
* ``inherit.aes``: If FALSE, overrides the default aesthetic, rather than combining with them. This is most useful for helper functions that define both data and aesthetics and shouldn’t inherit behaviour from the default plot specification.
distance
* Gap size between point and end of lines; use unit. Is converted to ’pt’ if given as simple numeric. When NULL or NA, gapping and shorten/treshold is disabled.
To keep the latter, set to 0.
shorten, threshold
When points are closer than threshold, shorten the line by the proportion in shorten instead of adding a gap by distance.
* ``lineend``: Line end style (round, butt, square).
* ``linejoin``: Line join style (round, mintre, bevel).
* ``linemitre``: Line mitre limit (number greater than 1).
* ``linesize``: Width of of line.
linecolour, linecolor
When not waiver(), the line is drawn with this colour instead of that set by
aesthetic colour.
* ``arrow``: Arrow specification, as created by arrow.
* ``...``: other arguments passed on to layer.

#### Examples

```{r}
# geom_point examples
library(ggplot2)
p <- ggplot(mtcars, aes(wt, mpg))
p + geom_point() + geom_line()
p + geom_pointline()
p + geom_pointline(linecolour='brown')
p + geom_pointpath()

```


```{r}
# Add aesthetic mappings
p + geom_pointline(aes(colour = factor(cyl)))
# Using linecolour preserved groups.
p + geom_pointline(aes(colour = factor(cyl)), linecolour='brown')
## If you want to combine the pretty lines of pointline that do *not* respect
## grouping (or order), combine several layers with geom_point on top:
p + geom_pointline() + geom_point(aes(colour=factor(cyl)))
#
```
```{r}
# Change scales
p + geom_pointline(aes(colour = cyl)) + scale_colour_gradient(low = "blue")
p + geom_pointline(aes(colour = cyl), linecolour='black') + scale_colour_gradient(low = "blue")
p + geom_pointline(aes(shape = factor(cyl))) + scale_shape(solid = FALSE)
```

 For shapes that have a border (like 21), you can colour the inside and  outside separately. Use the stroke aesthetic to modify the width of the  border
 
```{r}

ggplot(mtcars, aes(wt, mpg)) +
geom_pointline(shape = 21, colour = "black", fill = "white",
size = 5, stroke = 5, distance = unit(10, 'pt'))
```
```{r}
## Another example
df <- data.frame(x=rep(c('orange','apple','pear'), each=3),
b=rep(c('red','green','purple'), times=3), y=runif(9))
ggplot(df, aes(x=x, y=y, colour=b, group=b)) +
geom_pointline(linesize=1, size=2, distance=6) + theme_bw()
# geom_pointline() is suitable for time series
ggplot(economics, aes(date, unemploy)) + geom_pointline()
ggplot(economics_long, aes(date, value01, colour = variable)) +
geom_pointline()
````

#### Details

* geom_pointpath connects the observations in the same order in which they appear in the data.
* geom_pointline connects them in order of the variable on the x-axis.
* Both geom_pointpath and geom_pointline will only connect observations within the same group!
* However, if linecolour is not waiver(), connections will be made between groups, but possible in an incorrect order.

#### Aesthetics

geom_pointline and geom_pointpath understands the following aesthetics (required aesthetics
are in bold):
• x
• y
• alpha
• colour – sets colour of point. Only affects line if linecolour=waiver().
• stroke
• shape
• stroke
• group
• linetype
• size – only affects point size. Width of line is set with linesize and cannot be linked to an
aesthetic.
