---
title: "``gtable_show_grill``: Visualise underlying gtable layout."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
library(ggplot2)
```


#### Description
Visualises the table structure or the names of the gtable’s components.

#### Usage
<pre><code>
gtable_show_grill(x, plot = TRUE)

gtable_show_names(x, plot = TRUE, rect.gp = grid::gpar(col = "black", fill = "white", alpha = 1/4))
</code></pre>

#### Arguments

* ``x`` A gtable object. If given a ggplot object, it is converted to a gtable object with
ggplotGrob.
* ``plot`` Logical. When TRUE (default), draws resulting gtable object on a new page.
* ``rect.gp`` Graphical parameters (gpar) for background drop.



#### Examples

```{r}
library(ggplot2)
library(gtable)
library(grid)
p <- ggplot(mtcars, aes(wt, mpg)) + geom_point()
gtable_show_grill(p)
```

```{r}
library(ggplot2)
library(gtable)
library(grid)
p <- ggplot(mtcars, aes(wt, mpg)) + geom_point()
gtable_show_names(p)
```
#### Details

These functions are highly similar to gtable_show_layout. gtable_show_grill draws the grid
of the underlying table, and places row and column indicies in the margin. gtable_show_names
replaces the grobs with a semi-transparent rectangle and the components name.
#### Value
Modified gtable object, invisibly.
