---
title: "``guidebox_as_column``:  Guidebox as a column"
author: "Kevin O'Brien"
date: "11 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
library(ggplot2)
```

#### Description
Takes a plot or legend and returns a single guide-box in a single column, for embedding in e.g.
tables.

#### Usage

<pre><code>
guidebox_as_column(legend, which.legend = 1, add.title = FALSE)
</code></pre>

#### Arguments
* legend A ggplot2 plot or the legend extracted with g_legend. Do not provide a ggplotGrob
as it is indistinguisble from a legend.
* which.legend Integer, a legend can contain multiple guide-boxes (or vice versa?). Use this
argument to select which to use.
* add.title Does nothing yet.

#### Value
A gtable with keys and labels reordered into a single column and each pair of keys and labels in
the same cell.
See Also
g_legend

#### Examples

```{r}
library(ggplot2)
library(dplyr)
p <- ggplot(diamonds, aes(x=x, y=y, colour=cut)) + geom_point()
guidebox_as_column(p)
p <- p + guides(colour=guide_legend(ncol=2, byrow=TRUE))
guidebox_as_column(p)
```
