lemon_print



knitr extension: Always use ‘kable‘ for data frames.

#### Description

Convenience function for working with R Notebooks that ensures data frames (and dplyr tables) are
printed with kable while allowing RStudio to render the data frame dynamically for inline display.

#### Usage

lemon_print(x, options, ...)
## S3 method for class 'data.frame'
lemon_print(x, options, ...)
## S3 method for class 'table'
lemon_print(x, options, ...)

#### Arguments

x an data frame or dplyr table object to be printed
options Current chunk options are passed through this argument.
... Ignored for now.
Details
These functions divert data frame and summary output to kable for nicely printing the output.
For options to kable, they can be given directly as chunk-options (see arguments to kable), or
though as a list to a special chunk-option kable.opts.
For more examples, see vignette('lemon_print', package='lemon').remove_labels_from_axis
23
Knitr usage
To use for a single chunk, do
```{r render=lemon_print,caption='My data frame'}
data.frame
```
Note: We are not calling the function, but instead refering to it.
An alternate route for specifying kable arguments is as:
```{r render=lemon_print,kable.opts=list(align='l')}
data.frame
```
The option kable.opts takes precendence over arguments given directly as chunk-options.
To enable as default printing method for all chunks, include
knit_print.data.frame <- lemon_print
knit_print.table <- lemon_print
knit_print.grouped_df <- lemon_print # enableds dplyr results
knit_print.tibble <- lemon_print
knit_print.tbl <- lemon_print
Note: We are not calling the function, but instead assigning the knit_print functions for some
classes.
To disable, temporarily, specify chunk option:
```{r render=normal_print}`
data.frame
```
See Also
knit_print, kable
