---
title: "``currency``  Numeric vector with currency format"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(formattable)
```

#### Description
Numeric vector with currency format

#### Usage
<pre><code>
currency(x, symbol, digits, format = "f", big.mark = ",", ...)

## Default S3 method:
currency(x, symbol = "$", digits = 2L, format = "f",
big.mark = ",", ..., sep = "")

## S3 method for class 'character'
currency(x, symbol = get_currency_symbol(x),
         digits = max(get_digits(x)), format = "f", big.mark = ",", ...)
</code></pre>

#### Arguments
* ``x``: a numeric vector.
* ``symbol``: currency symbol
* ``digits``: an integer to indicate the number of digits of the percentage string.
* ``format``: format type passed to formatC.
* ``big.mark``: thousands separator
* ``...``: additional parameters passed to formattable.
* ``sep``: separator between symbol and value

#### Examples
```{r}
currency(200000)
currency(200000, "\U20AC")
currency(1200000, "USD", sep = " ")
currency(1200000, "USD", format = "d", sep = " ")
currency("$ 120,250.50")
currency("HK$ 120,250.50", symbol = "HK$")
currency("HK$ 120, 250.50")

```
