---
title: "``gradient`` Create a matrix from vector to represent colors in gradient"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(formattable)
```

#### Description

Create a matrix from vector to represent colors in gradient

#### Usage
<pre><code>
gradient(x, min.color, max.color, alpha = NULL, use.names = TRUE,na.rm = TRUE)
</code></pre>

#### Arguments
* ``x``: a numeric vector.
* ``min.color``: color of minimum value.
* ``max.color``: color of maximum value.
* ``alpha``: logical of whether to include alpha channel. NULL to let the function decide by 
input.
* ``use.names``: logical of whether to preserve names of input vector.
* ``na.rm``: logical indicating whether to ignore missing values as x is normalized. (default is TRUE)


####  Examples

```{r}
gradient(c(1,2,3,4,5), "white", "red")

gradient(c(5,4,3,2,1), "white", "red")

gradient(c(1,3,2,4,5), "white", "red")

gradient(c(1,3,2,4,5), rgb(0,0,0,0.5), rgb(0,0,0,1), alpha = TRUE)
```


#### Value

a matrix with rgba columns in which each row corresponds to the rgba value (0-255) of each element

in input vector x. Use csscolor to convert the matrix to css color strings compatible with web

browsers.

See Also

csscolor