
---
title: "``formattable::icontext``: "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(formattable)
```
## icontext Create icon-text elements

#### Description
Create icon-text elements

#### Usage
<pre><code>
icontext(icon, text = list(NULL), ..., simplify = TRUE,
provider = getOption("formattable.icon.provider", "glyphicon"),
class_template = getOption("formattable.icon.class_template",
"{provider} {provider}-{icon}"))
</code></pre>

#### Arguments
* ``icon``: a character vector or list of character vectors of icon names.
* ``text``: a character vector of contents.
* ``...``: additional parameters (reserved)
* ``simplify``: logical to indicating whether to return the only element if a single-valued list is resulted. 
* ``provider``: the provider of icon set.
* ``class_template``: a character value to specifiy to template of the class with ``"{provider}"`` to represent provider value and ``"{icon}"`` to represent icon values.

#### Examples
```{r}
icontext("plus")
icontext(c("star","star-empty"))
icontext(ifelse(mtcars$mpg > mean(mtcars$mpg), "plus", "minus"), mtcars$mpg)
icontext(list(rep("star",3), rep("star",2)), c("item 1", "item 2"))
```


See Also
Glyphicons in Bootstrap, Glyphicons
