---
title: "``formattable::style``: "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(formattable)
```

style Create a string-representation of CSS style

#### Description
Most HTML elements can be stylized by a set of CSS style properties. This function helps build
CSS strings using conventional argument-passing in R.

#### Usage
<pre><code>
style(...)
</code></pre>

#### Arguments
* ... style attributes in form of name = value. Many CSS properties contains '-' in the middle of their names. In this case, use "the-name" = value instead. NA will cancel the attribute.

#### Details
The general usage of CSS styling is
<span style = "color: red; border: 1px">Text</span>
The text color can be specified by ‘color‘, the border of element by ‘border‘, and etc.
Basic styles like color, border, background work properly and mostly consistently in modern
web browsers. However, some style properties may not work consistently in different browsers.

#### Value
a string-representation of css styles

#### See Also
List of CSS properties, CSS Reference

#### Examples
```{r}
style(color = "red")
style(color = "red", "font-weight" = "bold")
style("background-color" = "gray", "border-radius" = "4px")
style("padding-right" = "2px")
formattable(mtcars, list(
mpg = formatter("span",
style = x ~ style(color = ifelse(x > median(x), "red", NA)))))
```
