---
title: "``tabsort`` tabsort"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tbltools)
```

#### Description
Returns a sorted (descending) frequency tbl

#### Usage
<pre><code>
tabsort(.data, ..., prop = TRUE, na_omit = TRUE, sort = TRUE)
ntbl(.data, ...)
</code></pre>

#### Arguments
* ``.data``: Data
* ``...``: Unquoted column names of variables to include in table. Default is to use all columns.
* ``prop``: Logical indicating whether to include a proportion of total obs column.
* ``na_omit``: Logical indicating whether to exclude missing. If all responses are missing, a missing value is used as the single category.
* ``sort``: Logical indicating whether to sort the returned object.


#### Examples
```{r}
## generate example data
x <- sample(letters[1:4], 200, replace = TRUE)
y <- sample(letters[5:8], 200, replace = TRUE)
## count and sort frequencies for each vector
tabsort(x)
tabsort(y)
## combine x and y into data frame
dat <- data.frame(x, y)
## select columns and create freq table
tabsort(dat, x)
tabsort(dat, x, y)
```

####Value
Frequency tbl