---
title: "``greg::confint.ols``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(greg)
```

confint.ols A confint function for the ols

#### Description 

This function checks that there is a df.residual before running the qt(). If not found it then defaults
to the qnorm() function. Otherwise it is a copy of the confint() function.

#### Usage
<pre><code>
## S3 method for class 'ols'
confint(object, parm, level = 0.95, ...)
</code></pre>

#### Arguments
object a fitted ols-model object.
parm a specification of which parameters are to be given confidence intervals, either
a vector of numbers or a vector of names. If missing, all parameters are considered.
level the confidence level required.
... additional argument(s) for methods.

#### Examples
```{r}
# Generate some data
n <- 500
x1 <- runif(n)*2
x2 <- runif(n)
y <- x1^3 + x2 + rnorm(n)
library(rms)
library(sandwich)
dd <- datadist(x1, x2, y)
org.op <- options(datadist = "dd")
```


```{r}
# Main function
f <- ols(y ~ rcs(x1, 3) + x2)
```


```{r}
# Check the bread
bread(f)
# Check the HC-matrix
vcovHC(f, type="HC4m")
```


```{r}
# Adjust the model so that it uses the HC4m variance
f_rob <- robcov_alt(f, type="HC4m")
# Get the new HC4m-matrix
# - this function just returns the f_rob$var matrix
```


```{r}
vcov(f_rob)
# Now check the confidence interval for the function
confint(f_rob)
options(org.op)
```




#### Value
A matrix (or vector) with columns giving lower and upper confidence limits for each parameter.
These will be labelled as (1-level)/2 and 1 - (1-level)/2 in

