---
title: "``greg::confint_robust ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(greg)
```
The confint function adapted for vcovHC

#### Description 

The confint.lm uses the t-distribution as the default confidence interval estimator. When there is reason to believe that the normal distribution is violated an alternative approach using the ``vcovHC()`` may be more suitable.

#### Usage
<pre><code>
confint_robust(object, parm, level = 0.95, HC_type = "HC3",
t_distribution = FALSE, ...)
</code></pre>

#### Arguments
* ``object``: The regression model object, either an ols or lm object
* ``parm``: a specification of which parameters are to be given confidence intervals, either a vector of numbers or a vector of names. If missing, all parameters are considered.
* ``level``: the confidence level required.
* ``HC_type``: See options for ``vcovHC()``
* ``t_distribution``: A boolean for if the t-distribution should be used or not. Defaults to FALSE. According to Cribari-Nieto and Lima’s study from 2009 this should not be the
case.
* ``...``: Additional parameters that are passed on to vcovHC()


#### Examples
```{r}
n <- 50
x <- runif(n)
y <- x + rnorm(n)
fit <- lm(y~x)
library("sandwich")
confint_robust(fit, HC_type = "HC4m")
```


#### Value
matrix A matrix (or vector) with columns giving lower and upper confidence limits for each parameter.
These will be labelled as (1-level)/2 and 1 - (1-level)/2 in
References
F. Cribari-Neto and M. da G. A. Lima, "Heteroskedasticity-consistent interval estimators", Journal
of Statistical Computation and Simulation, vol. 79, no. 6, pp. 787-803, 2009.
