---
title: "``coord_capped_cart``: Cartesian coordinates with capped axis lines."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lemon)
library(ggplot2)
```

Caps the axis lines to the outer ticks to e.g. indicate range of values. 
Methods correspond to ``coord_cartesian`` and ``coord_flip``

### Usage
<pre><code>
coord_capped_cart(xlim = NULL, ylim = NULL, expand = TRUE,
  top = waiver(), left = waiver(), bottom = waiver(),
  right = waiver(), gap = 0.01)

coord_capped_flip(xlim = NULL, ylim = NULL, expand = TRUE,
  top = waiver(), left = waiver(), bottom = waiver(), 
  right = waiver(), gap = 0.01)

capped_horizontal(capped = c("both", "left", "right", "none"), gap = 0.01)
capped_vertical(capped = c("top", "bottom", "both", "none"),gap = 0.01)
</code></pre>

#### Arguments
* xlim, ylim: Limits for the x and y axes.
* expand: If TRUE, the default, adds a small expansion factor to the limits to ensure that data and axes don't overlap. If FALSE, limits are taken exactly from the data or xlim/ylim.
* top, left, bottom, right: Either a function returned from capped_horizontal or brackets_horizontal.
If string, it is assumed to be shorthand for capped_horizontal(capped) or similar for vertical.
* gap Both ends are always capped by this proportion. Usually a value between 0 and 1.
* capped Which end to cap the line. Can be one of (where relevant): both, none, left, right, top, bottom.



####Examples
```{r}
library(ggplot2)
# Notice how the axis lines of the following plot meet in the lower-left corner.
p <- ggplot(mtcars, aes(x = mpg)) + geom_dotplot() +
theme_bw() +
theme(panel.border=element_blank(), axis.line=element_line())
p
# We can introduce a gap by capping the ends:
p + coord_capped_cart(bottom='none', left='none')
#
#
#

```
The lower limit on the y-axis is 0. We can cap the line to this value.
Notice how the x-axis line extends through the plot when we no long
define its capping.

```{r}
p+ coord_capped_cart(left='both')
# It it also works on the flipped.
p + coord_capped_flip(bottom='both')
```

```{r}
# And on secondary axis, in conjuction with brackets:
p + scale_y_continuous(sec.axis = sec_axis(~.*100)) +
scale_x_continuous(sec.axis = sec_axis(~1/., name='Madness scale')) +
coord_capped_cart(bottom='none', left='none', right='both', top=brackets_horizontal())
# Although we cannot recommend the above madness.
```

#### Details

This function is a simple override of ``coord_flex_cart`` and ``coord_flex_flip``, which allows short-hand specification of what to cap.

A panel-border is typically drawn on top such that it covers tick marks, grid lines, and axis
lines. Many themes also do not draw axis lines. To ensure the modified axis lines are visible, use
theme(panel.border=element_blank(), axis.lines=element_line()).
