---
title: "``furniture::long``"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(furniture)
```


## Wide to Long Data Reshaping

#### Description

``long()`` is a wrapper of ``stats::reshape()`` that takes the data from a wide format to a long format.
It can also handle unbalanced data (where some measures have different number of "time points").

#### Usage
<pre><code>
long(data, ..., v.names = NULL, id = NULL, timevar = NULL,
times = NULL, sep = "")
</code></pre>

#### Arguments
* ``data``: the data.frame containing the wide format data
* ``...``: the variables that are time-varying that are to be placed in long format, needs to be in the format ``c("x1", "x2"), c("z1", "z2")``, etc.. 
  If the data is unbalanced (e.g., there are three time points measured for one variable but only two for another), using the placeholder variable miss, helps fix this.
* ``v.names``: a vector of the names for the newly created variables (length same as number of vectors in varying)
* ``id``: the ID variable in quotes
* ``timevar``: the column with the "time" labels
* ``times``: the labels of the timevar (default is numeric)
* ``sep``: the separating character between the wide format variable names (default is ""); e.g. "x1" and "x2" would create the variable name of "x"; only applicable if v.names

#### Examples

```{r}
x1  <- runif(1000)
 x2 <- runif(1000)
 x3 <- runif(1000)
 y1 <- rnorm(1000)
 y2 <- rnorm(1000)
 z <- factor(sample(c(0,1), 1000, replace=TRUE))
 a <- factor(sample(c(1,2), 1000, replace=TRUE))
 b <- factor(sample(c(1,2,3,4), 1000, replace=TRUE))
 df <- data.frame(x1, x2, x3, y1, y2, z, a, b)

```

```{r}
## "Balanced" Data
ldf1 <- long(df, c("x1", "x2"), c("y1", "y2"), v.names = c("x", "y"))
```

```{r}
## "Unbalanced" Data
ldf2 = long(df, c("x1", "x2", "x3"), c("y1", "y2", "miss"), v.names = c("x", "y"))
```
#### Author(s)
Tyson S. Barrett

#### See Also
``stats::reshape()`` and ``sjmisc::to_long()``
