---
title: "``mutate_rowsums``: Get Row Sums within a Pipe"
author: "Kevin O'Brien"
date: "11 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(furniture)
```






#### Description

Does what ``rowSums()`` does can be used one its own without ``dplyr::mutate()`` within a pipe.

#### Usage
<pre><code>
mutate_rowsums(data, new_var, ..., na.rm = FALSE)
</code></pre>

#### Arguments
* ``data``: the dataframe that contains the variables to get the row means from
* ``new_var``: the name of the new variable for which you’ll put the row means in quotes
* ``...``: the variables (unquoted) to be included in the row means
* ``na.rm``: should the missing values be ignored? default is FALSE

#### Value
the row means included within the data.frame

### Examples
```{r}
## Not run:
library(furniture)
library(tidyverse)
data <- data.frame(
x = sample(c(1,2,3,4), 100, replace=TRUE),
y = rnorm(100),
z = rnorm(100)
)
data2 <- data %>%
mutate_rowsums("y_z_sums", y, z)

data2 <- data %>%
mutate_rowsums("y_z_sums", y, z, na.rm=TRUE)
## End(Not run) 

``` 
