---
title: "``tableC``: Correlation Table" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(furniture)
library(ggplot2)
```

#### Description

Correlations printed in a nicely formatted table.

#### Usage

<pre><code>
tableC(.data, ..., cor_type = "pearson", na.rm = FALSE, rounding = 3, output = "text", booktabs = TRUE, caption = NULL, align = NULL, float = "htb")
</code></pre>

#### Arguments
* ``.data`` : the data frame containing the variables
* ``...`` : the unquoted variable names to be included in the correlations
* ``cor_type`` : the correlation type; default is "pearson", other option is "spearman"
* ``na.rm`` : logical (default is FALSE); if set to TRUE, the correlations use the "complete.obs"methods option from stats::cor()
* ``rounding`` : the value passed to round for the output of both the correlation and p-value; default is 3
* ``output`` : how the table is output; can be "text" for regular console output, "latex2" for specialized latex output, or any of kable()'s options from knitr (e.g., "latex", "markdown", "pandoc").
* ``booktabs``: when output != "text"; option is passed to knitr::kable
* ``caption``: when output != "text"; option is passed to knitr::kable
* ``align``: when output != "text"; option is passed to knitr::kable
* ``float``: when output == "latex2" it controls the floating parameter (h, t, b, H)

```{r}
tableC(iris[,1:4],outut=text) 
```
