---
title: "``washer``: Wash Your Data"
author: "Kevin O'Brien"
date: "11 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(furniture)
library(ggplot2)
```



#### Description

Washes the data by replacing values with either NA’s or other values set by the user. Useful for
replacing values such as 777’s or 999’s that represent missing values in survey research. Can also
perform many useful functions on factors (e.g., removing a level, replacing a level, etc.)

#### Usage

<pre><code>
washer(x, ..., value = NA)
</code></pre>

#### Arguments

* ``x`` : the variable to have values adjusted
* ``...`` : the values in the variable that are to be replaced by either NAs or the value set by the user. Can be a function (or multiple functions) to specify values to change (e.g., is.nan(), is.na()).
* ``values``: (optional) if specified, the values in ... will be replaced by this value (must be a single value)wide
the original vector (although if the original was a factor, it was changed to a character) with the values changed where indicated.

#### Examples

```{r}
x = c(1:20, NA, NaN)
washer(x, 9, 10)
washer(x, 9, 10, value=0)
washer(x, 1:10)
washer(x, is.na, is.nan, value=0)
washer(x, is.na, is.nan, 1:3, value=0)
```
